PANCHANGE_analysis

### 2020-08-24 PANCHANGE_analysis.Rmd
added pcl percentages and made changes to the preprocessing script

```{r descriptives gad.diff_score_cols}
gad.numeric_table <- dat %>% 
#  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = gad.diff_score_base_prepan,
      "Base - retro" = gad.diff_score_base_retro,
      "Prepan - retro" = gad.diff_score_prepan_retro,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r gad percentage plot prepan_retro}
dat.long.gad.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r gad percentage plot prepan_retro}
dat.long.gad.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

```{r gad plot prepan_retro diff}
dat.long.gad.diff %>%
  filter(Time_point == "prepan_retro") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

@@

```{r descriptives phq.diff_score_cols}
phq.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = phq.diff_score_base_prepan,
      "Base - retro" = phq.diff_score_base_retro,
      "Prepan - retro" = phq.diff_score_prepan_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r phq percentage plot prepan_retro}
dat.long.phq.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r phq plot prepan_retro diff}
dat.long.phq.diff %>%
  filter(Time_point == "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

@@

```{r descriptives ocir.diff_score_cols}
ocir.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = ocir.diff_score_base_prepan,
      "Base - retro" = ocir.diff_score_base_retro,
      "Prepan - retro" = ocir.diff_score_prepan_retro,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r ocir percentage plot prepan_retro}
dat.long.ocir.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r ocir plot prepan_retro diff}
dat.long.ocir.diff %>%
  filter(Time_point == "prepan_retro") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

@@

```{r RUBBISH 1}
gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_prepan_retro_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_retro)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar() +
  theme_minimal()

@@

```{r RUBBISH 2 fig.height=5, fig.width=5}
gad.diff_score_prepan_base_plot /
  gad.diff_score_prepan_retro_plot /
  gad.diff_score_prepan_base_plot +
  plot_layout(guides = "collect", heights = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```

@@

For each item 
present percentages of how say that this is due to the pandemic 
```{r}

>>>>

```{r descriptives gad.diff_score_cols}
gad.numeric_table <- dat %>% 
#  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = gad.diff_score_base_prepan,
      "Base - retro" = gad.diff_score_base_retro,
      "Prepan - retro" = gad.diff_score_retro_prepan,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r gad percentage plot retro_prepan}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r gad percentage plot retro_prepan}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

```{r gad plot retro_prepan diff}
dat.long.gad.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

@@

```{r descriptives phq.diff_score_cols}
phq.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = phq.diff_score_base_prepan,
      "Base - retro" = phq.diff_score_base_retro,
      "Prepan - retro" = phq.diff_score_retro_prepan
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r phq percentage plot retro_prepan}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r phq plot retro_prepan diff}
dat.long.phq.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

@@

```{r descriptives ocir.diff_score_cols}
ocir.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = ocir.diff_score_base_prepan,
      "Base - retro" = ocir.diff_score_base_retro,
      "Prepan - retro" = ocir.diff_score_retro_prepan
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r ocir percentage plot retro_prepan}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r ocir plot retro_prepan diff}
dat.long.ocir.diff %>%
  filter(Time_point == "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

@@

```{r RUBBISH 1}
gad.diff_score_base_prepan_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_base_prepan)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_retro_prepan_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_retro_prepan)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_base_retro_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_base_retro)) +
  geom_bar() +
  theme_minimal()

@@

```{r RUBBISH 2 fig.height=7, fig.width=5}
gad.diff_score_base_prepan_plot /
  gad.diff_score_retro_prepan_plot /
  gad.diff_score_base_retro_plot +
  plot_layout(guides = "collect", heights = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```

@@

For each item 
present percentages of how say that this is due to the pandemic 
```{r}
pcl.retro.items <- c(
  "pcl.stressful_experience_upset_reminded_retro_numeric",
  "pcl.stressful_experience_repeated_images_retro_numeric",
  "pcl.stressful_situation_avoiding_activities_retro_numeric",
  "pcl.cut_people_feeling_distant_retro_numeric",
  "pcl.difficulty_concentrating_retro_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric"
)

pcl.percentages.summary <- dat %>%
  select(
    all_of(pcl.retro.items)
  ) %>%
  gather(
    key = "PCL Item",
    value = "Binary_score",
    all_of(pcl.retro.items)
  ) %>%
  mutate(Binary_score = fct_explicit_na(as.factor(Binary_score), na_level = "Missing")) %>%
  group_by(`PCL Item`) %>%
  count(`PCL Item`, Binary_score) %>%
  mutate(prop = round(n/sum(n), 3)*100) %>%
  mutate(n_prop = paste0(n," (",prop, "%)"))

pcl.percentages.summary
```
